MLH1 Data Report

### 2019-12-27 doc/Main_Report_Results.rmd
adding thoughts for variance section

The **biological significance** of within mouse variance in CO per cell is...

@@

@@

>>>>

in addition to the mean gwRR, the variance is also an important metric to dicribe

Within animal variance in CO count / genome wide RR is important because it could shape constraints (and determine how effective stabilizing selection can act (ref))

@@

RW's main qtl paper used the within animal variance, 
"We mapped QTL for
MLH1 count variance within individuals, applying an approach
to deconvolve the mean-variance relationship (see
Materials and Methods)."

above method remove / accounts for mean-variance correlation -

The fig5 also has a histogram of within animal variances in MLH1 counts (For F2s, with the parents as reference) (I could do this for males and females)

QTL on chrm 14, decreased variance in GG genotype, compared to hetZ and WSB (I think this also raised the mean)

@article{wang2017genetics,
  title={Genetics of genome-wide recombination rate evolution in mice from an isolated Island},
  author={Wang, Richard J and Payseur, Bret A},
  journal={Genetics},
  volume={206},
  number={4},
  pages={1841--1852},
  year={2017},
  publisher={Genetics Soc America}
}

references for phenotypic variance connected to robustness to environment, increase in developmental consistancy
Waddington 1942, Rutherford and Lindquist 2998, Mackay and Lyman 2005, Levy and Siegal 2008)

phenotypic variance leading to adaptation - 
(Losick and desplan 2008, Beaumont 2009, Eldar and Eloqitz 2010)

Previous vQTLs (Shen etal 2012, Hulse and Cai 2013, Mulder et al 2016)

meiotic Checkpoints for ensuring consistancy (Hochwagen and Amon 2006, Li and Schimenti 2007, Jaramillo-Lambert 2010 and Kauppi 2013)

@@

```{r variance.hist, echo=FALSE}

### modeling variance
